---
title: "two_sample_t_test"
output: html_document
---
# Summary
1. Use f-test (variance test) to see if variance is similar between the two samples. 
  * If variance is the same (p > 0.05), it means that we can use t-test to check if the means of the samples are the same.
  * If variance is not the same, it means that we don't have enough data OR that the variance of the two samples are not the same, which means that we cannot use t-test.
    * This is when Monte Carlo may be useful, i.e. not having enough data
  
2. Use chi-squared test for A/B testing

3. Beta distribution & Dirichlet distribution for Monte Carlo
  * Beta distribution is for binary discrete events (e.g. user clicked vs. didn't click on ads). Use beta distribution when there are only 2 potential outcomes.
  * Dirichlet distribution is the multidimensional generalisation of the beta distribution. Use Dirichlet distribution when > 2 outcomes
  
  
4. Add Bayesian prior before running Monte Carlo
  
## 1. F-test and t-test
```{r}
sample_1 <-rnorm(10000)
sample_2 <-rnorm(10000)

var.test(sample_1, sample_2) # f-test
```

```{r}
t.test(sample_1,sample_2)
```

```{r}
sample_1 <-rnorm(10000)
sample_2 <-runif(10000)

var.test(sample_1,sample_2)
t.test(sample_1,sample_2)
```

## 2. chi-squared test for A/B testing
`chisq.test(x,y)` where:
x = vector of control group
y = vector of outcomes associated with x
x and y must be same length
```{r}
df<-read.csv("https://goo.gl/j6lRXD")
head(df)
```

## 3. Beta Distribution in Monte Carlo
Use it for binary discrete events. 

`rbeta(runs, shape1,shape2)` where:
* shape1 = one outcome (e.g. "clicked")
* shape2 = another outcome (e.g. "not clicked")
```{r}
runs <- 1000
experiment_1<-rbeta(runs, shape1, shape2)
experiment_2<-rbeta(runs, shape1, shape2)
```

## 4. Dirichlet Distribtion
Dirichlet Distribution is the multidimensional generalization of the beta distribution. 
a = vector for one outcome, b = vector for another outcome, etc. 

```{r}
runs<-100
experiment_1 <-rdirichlet(runs,alpha=c(a,b,n))
experiment_2 <-rdirichlet(runs,alpha=c(a,b,n))
```

binary A/B testing with categorical outcomes

Raw table's format:

|Index|model version| performance improved (yes/no)
|1    | 1           | yes                    |
|2    | 1           | no                     |
|3    | 2           | yes                    |
|4    | 2           | no                     | 


Aggregated table's format:

|Model Version| Improved    | Didn't improve |
|1            | 30          | 36             |
|2            | 12          | 10             |

```{r}
runs<-10000
model_1<-rbeta(runs,30,36) # 30 is number of rows where things are improved, 36 is the number of rows where things did not improve for model 1
model_2<-rbeta(runs,12,10) 

perc_model1_superior<-sum(model_1>model_2) /runs
perc_model1_superior
```


## 5. Add a Bayesian prior into Beta Distribution
`rbeta(runs,shape1+prior1,shape2+prior2)` 

```{r}
runs<-1000

alpha_prior<-15
beta_prior<-18

model_1 <-rbeta(runs, 30 + alpha_prior, 36 + beta_prior)
model_2 <-rbeta(runs, 12 + alpha_prior, 10 + beta_prior)

prob_model1_is_superior <- sum(model_1>model_2)/runs
prob_model1_is_superior
```
